First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-07-19 paper/paper.tex
Church encoding section

\subsection{Connection to Church encodings}
\begin{todo}
  Write this subsection
\end{todo}

>>>>

\subsection{Connection to Church encodings}
\begin{todo}
  Work on this subsection
\end{todo}

Algebraic datatypes can be represented as lambda calculus terms using
\textit{Church encodings}. For example, the pair constructor can be
represented as

\begin{lstlisting}
church_mkPair
  :: a -> b -> (a -> b -> r) -> r
church_mkPair = \ x y f -> f x y
\end{lstlisting}

with the eliminators

\begin{lstlisting}
church_fst :: ((a -> b -> a) -> r) -> r
church_fst = \ p -> p (\ x y -> x)

church_snd :: ((a -> b -> b) -> r) -> r
church_snd = \ p -> p (\ x y -> y)
\end{lstlisting}

Coproducts can be represented with the constructors

\begin{lstlisting}
church_mkLeft
  :: a -> (a -> r) -> (b -> r) -> r
church_mkLeft = \ x f g -> f x

church_mkRight
  :: b -> (a -> r) -> (b -> r) -> r
church_mkRight = \ y f g -> g y
\end{lstlisting}

and the eliminator

\begin{lstlisting}
church_eitherElim
  :: (a -> b -> r) -> a -> b -> r
church_eitherElim = \ e f g -> e f g
\end{lstlisting}

In this representation:

\begin{itemize}
  \item A pair of type \ttt{A} and type \ttt{B} is represented with a value of type
\ttt{forall r. (A -> B -> r) -> r}.

  \item A coproduct of type \ttt{A} and type \ttt{B} is represented with a value of type
\ttt{forall r. (A -> r) -> (B -> r) -> r}.
\end{itemize}

More generally, an algebraic datatype can be thought of as a sum of products
(that is, a coproduct of products).

\begin{todo}
  Maybe it could make sense to essentially derive the pattern matching representation
  from this Church encoding. If so, this could be described around here.
\end{todo}
